---
title: "Factor Analysis in Short Version of FSS-2"
author: Geiser Chalco Challco <geiser@alumni.usp.br>
output:
  github_document: default
  word_document: default
  html_document: default
  pdf_document:
    keep_tex: true
fontsize: 10pt
---

* Data: [data/raw-data.csv](data/raw-data.csv)
* Source code: [02-factor-analysis-short-FSS.Rmd](02-factor-analysis-short-FSS.Rmd)

```{r setup, include=FALSE, echo=FALSE}
wants <- c('readr','dplyr','psych','lavaan','ggraph','semPlot','robustHD','GPArotation','parameters')
has <- wants %in% rownames(installed.packages())
if (any(!has)) install.packages(wants[!has])

knitr::opts_chunk$set(echo = TRUE)
defaultW <- getOption("warn")
options(warn = -1)
```

## Loading libs

```{r,message=FALSE}
library(GPArotation)
library(readr)
library(dplyr)
library(psych)
library(lavaan)
library(ggraph)
library(semPlot)
library(MVN)
library(daff)
library(robustHD)
library(parameters)
```

## Loading data

* As in the identification of [careless](00-careless.md), there was only 2 data, we decided to use all the raw data.

```{r}
raw_data <- read.csv("data/raw-data.csv")
dat <- select(raw_data, starts_with("gender"), starts_with("age"), starts_with("Q"))
datItem <- select(dat, starts_with("Q"))
```

## Confirmatory Factorial Analisis (CFA)

Setting a list of models in the list variable "mdls" to be tested using lavaan SEM syntax.

```{r}
mdls <- c('original short FSS-2'='
FSS =~ Q19+Q29+Q12+Q22+Q32+Q24+Q34+Q17+Q36
', 
'alternative short FSS-2'='
FSS =~ Q10+Q11+Q30+Q4+Q23+Q24+Q7+Q26+Q27
',
'alternative min short FSS-2'='
FSS =~ Q19+Q11+Q30+Q4+Q32+Q24+Q7+Q17+Q36
')
```

Perform CFA in all the defined models and obtain the fit measurements in the variable "*cfa_results*"

```{r echo=FALSE}
cfa_results <- lapply(mdls, FUN = function(x) {
  cfa <- cfa(x, data=datItem, std.lv=T, estimator="WLSMV", meanstructure=T)
  fit <- round(fitMeasures(cfa), 3)
  fit <- c(
    fit
    , 'rmsea.ci' = paste0('[',fit['rmsea.ci.lower'],'; ',fit['rmsea.ci.upper'],']')
    , 'rmsea.ci.scaled' = paste0('[',fit['rmsea.ci.lower.scaled'],'; ',fit['rmsea.ci.upper.scaled'],']')
    , 'rmsea.ci.robust' = paste0('[',fit['rmsea.ci.lower.robust'],'; ',fit['rmsea.ci.upper.robust'],']')
    , 'cfi.obs' = ifelse(fit[['cfi']] < 0.85, 'unacceptable fit', NA)
    , 'cfi.obs.scaled' = ifelse(fit[['cfi.scaled']] < 0.85, 'unacceptable fit', NA)
    , 'cfi.obs.robust' = ifelse(fit[['cfi.robust']] < 0.85, 'unacceptable fit', NA)
    , 'tli.obs' = ifelse(fit[['tli']] < 0.85, 'unacceptable fit', NA)
    , 'tli.obs.scaled' = ifelse(fit[['tli.scaled']] < 0.85, 'unacceptable fit', NA)
    , 'tli.obs.robust' = ifelse(fit[['tli.robust']] < 0.85, 'unacceptable fit', NA)
    , 'rmsea.obs' = ifelse(fit[['rmsea']] > 0.10, 'poor fit', NA)
    , 'rmsea.obs.scaled' = ifelse(fit[['rmsea.scaled']] > 0.10, 'poor fit', NA)
    , 'rmsea.obs.robust' = ifelse(fit[['rmsea.robust']] > 0.10, 'poor fit', NA)
  )
  list(cfa = cfa, fit = fit)
})
```

Print the basic fit measures for all the CFA models.

```r
do.call(rbind, lapply(cfa_results, FUN = function(x) {
  x$fit[c('chisq','df','cfi','tli','rmsea','rmsea.ci','cfi.obs','tli.obs','rmsea.obs')]
}))
```

```{r echo=FALSE}
knitr::kable(do.call(rbind, lapply(cfa_results, FUN = function(x) {
  x$fit[c('chisq','df','cfi','tli','rmsea','rmsea.ci','cfi.obs','tli.obs','rmsea.obs')]
})))
```


Calculate fit measures for all the CFA models.

```r
t(do.call(rbind, lapply(cfa_results, FUN = function(x) x$fit)))
```

```{r, echo=FALSE}
knitr::kable(t(do.call(rbind, lapply(cfa_results, FUN = function(x) x$fit))))
```


### Summarize and draw diagrams of CFA models without negative observations

Select CFA models without negative observations

```{r}
(mdls <- names(cfa_results)[sapply(cfa_results, FUN = function(x) {
  all(is.na(x$fit[c('cfi.obs','tli.obs','rmsea.obs')]))
})])
```

Print summaries and diagrams for the CFA models without negative observations

```{r, fig.height=8, fig.width=8}
for (mdl in mdls) {
  cat(mdl,"\n"); summary(cfa_results[[mdl]]$cfa, standardized = T)
  semPaths(cfa_results[[mdl]]$cfa,  "std"
           , curvePivot = T, layout = "circle", rotation = 1, fade = F, intercepts = F, residuals = F
           , sizeLat = 4, sizeLat2 = 3, sizeMan = 4, sizeMan2 = 2, curvature = 2.5, esize = 1.5, asize = 1.5
           , edge.label.cex = 0.35, edge.label.position = 0.5)
}
```

### Summarize comparison between CFA models without negative observations

```{r}
combn(mdls, 2, simplify = F, FUN = function(x) {
  lavTestLRT(cfa_results[[x[1]]]$cfa, cfa_results[[x[2]]]$cfa, model.names=x)
})
```

> *Note*: Significant difference Pr(>Chisq) indicates that:
> The model1 fits the gathered data significantly different (better/worse) than the model2


```{r include=FALSE}
options(warn = defaultW)
```
