---
title: "Factor Analysis of FSS-BR"
author: Geiser Chalco Challco <geiser@alumni.usp.br>
output:
  github_document:
    toc: true
    toc_depth: 3
  word_document: default
  html_document: 
    toc: true
    toc_depth: 3
    theme: default
    highlight: default
  pdf_document:
    keep_tex: true
fontsize: 10pt
---

# Prerequisites

* R-script: [script.R](script.R)
* DataSet: [data-fss.csv](data-fss.csv) OR [fss2-data.xlsx](fss2-data.xlsx)

## Loading libs, functions and data

```{r setup, include=FALSE, echo=FALSE}
knitr::opts_chunk$set(echo = TRUE)
defaultW <- getOption("warn")
options(warn = -1)
```

Loading needed libs (packages)

```{r, message=FALSE}
wants <- c('psych', 'dplyr','readxl','psy','olsrr','MVN','parameters')
has <- wants %in% rownames(installed.packages())
if (any(!has)) install.packages(wants[!has])
options("mc.cores"=parallel::detectCores())

if (!'OpenMx' %in% rownames(installed.packages())) {
#  source('https://vipbg.vcu.edu/vipbg/OpenMx2/software/getOpenMx.R')
}

library(readr)
library(dplyr)
library(psych)
library(lavaan)
library(olsrr)
library(semTools)
library(mirt)
```

Loading data

```{r}
if (!file.exists("data-fss.csv")) {
  library(readxl)
  fss <- read_excel("fss2-data.xlsx", sheet = "raw-data")
  write_csv(fss[!fss$is_invalid,], "data-fss.csv")
}
raw_data <- read.csv("data-fss.csv")
fss <- as.data.frame(sapply(select(raw_data, starts_with("Q")), as.integer))
```

## Loading functions

```{r}
getFactors <- function(fit, secondFactor = NULL) {
  sl <- standardizedSolution(fit)
  sl <- sl[sl$op == '=~',]
  lfactors <- lapply(unique(sl$lhs), FUN = function(lhs) {
    sl$rhs[sl$lhs == lhs] 
  })
  names(lfactors) <- unique(sl$lhs)
  if (!is.null(secondFactor))
    lfactors[[secondFactor]] <- NULL
  return(lfactors)
}

#' Calculate composite reliability of factors
#'
#' This functions calculate composite reliability values of factors
#'
#' @param fit a lavaan object expected to contain a CFA model
#' @param return.total logical indicating whether to return a final column containing the reliability of a composite of all items.
#' @return Reliability values of each factor in each group.
compReliability <- function(fit, return.total = F) {
  toReturn <- sapply(getFactors(fit), FUN = function(x) {
    sl <- standardizedSolution(fit)
    sl <- sl$est.std[sl$op == "=~" & sl$rhs %in% x]
    names(sl) <- x
    
    re <- 1 - sl^2
    sum(sl)^2 / (sum(sl)^2 + sum(re))
  })
  if (return.total) {
    sl <- standardizedSolution(fit)
    sl <- sl$est.std[sl$op == "=~"]
    re <- 1 - sl^2
    toReturn <- c(toReturn, total=sum(sl)^2 / (sum(sl)^2 + sum(re)))
  }
  toReturn
}

#' Asessing convergent and discriminant validity
#'
#' This functions assess the discriminant and convergent validity of factors 
#' based on Heterotrait-Monotrait Ratio (semTools::htmt).
#'
#' @param fit a lavaan object expected to contain a CFA model
#' @param lnv string with the lavaan syntax of the fit CFA model.
#' @param dat data.frame with the data used in the CFA model
#' @param secondFactor second factor to be used in the CFA model
#' @return Composite Reliability, AVE and matrix of Heterotrait-Monotrait Ratio
convergentDiscriminantValidity <- function(fit, lvn, dat, secondFactor = NULL) {
  library(olsrr)
  library(semTools)
  
  CR <- compReliability(fit)
  AVE <- reliability(fit)[c("avevar"),]
  if (!is.null(secondFactor)) {
    AVE[secondFactor] <- reliability(fit, return.total = TRUE)["avevar","total"]
  }
  
  factors <- getFactors(fit, secondFactor)
  
  for (f1 in names(factors)) dat[[f1]] <- rowSums(dat[,factors[[f1]]])
  if (is.null(secondFactor)) secondFactor <- 'F0'
  dat[[secondFactor]] <- rowSums(dat[,names(factors)])
  
  mdl <- lm(as.formula(paste0(secondFactor,' ~ ', paste0(names(factors), collapse = '+'))), data = dat)
  VIF <- ols_vif_tol(mdl)$VIF
  VIF.i <- sapply(names(factors), FUN = function(f1) {
    mdl <- lm(as.formula(paste0(f1,' ~ ',paste0(factors[[f1]], collapse = '+'))), data = dat)
    max(ols_vif_tol(mdl)$VIF)
  })
  
  
  lvn2 <- stringr::str_replace(lvn, paste0("\n\\s*",secondFactor,"\\s*.*=~\\s*.*\n","\n"),"\n\n")
  corr.df <- as.table(inspect(fit, "cor.lv"))
  corr.df[upper.tri(corr.df)] <- NA
  htmt.df <- as.table(semTools::htmt(lvn2, dat))
  if (is.null(secondFactor) || secondFactor != 'F0') {
    cnames <- colnames(htmt.df)
    htmt.df <- cbind(htmt.df, rep(NA, nrow(htmt.df)))
    htmt.df <- rbind(htmt.df, rep(NA, ncol(htmt.df)))
    rownames(htmt.df) <- c(cnames, secondFactor)
    colnames(htmt.df) <- c(cnames, secondFactor)  
  }
  htmt.df[lower.tri(htmt.df)] <- NA
  
  df <- corr.df
  df[upper.tri(corr.df)] <- htmt.df[upper.tri(df)]
  for (cname in names(AVE)) df[cname,cname] <-  sqrt(AVE[[cname]])
  
  as.data.frame(cbind(CR,AVE, VIF, VIF.i, df))
}

#' Summarize fit indexes of CFA models
#'
#' This functions summarize fit indexes from CFA models
#'
#' @param fits a list of lavaan objects with CFA models
#' @return fit indexes results of CFA models
summariseFits <- function(fits) {
 df_fit <- do.call(rbind, lapply(fits, FUN = function(fit) {
  dat <- as.list(round(fitMeasures(fit, c("chisq","df","cfi","tli","srmr","rmsea","rmsea.ci.lower","rmsea.ci.upper")), 3))
  rbind(c(dat[c("chisq","df")],"chisq/df"=round(dat$chisq/dat$df,3)
          , dat[c("cfi","tli","srmr","rmsea")]
          , "rmsea.ci" = paste0("[",dat$rmsea.ci.lower,"; ",dat$rmsea.ci.upper,"]")))
  }))
 rownames(df_fit) <- names(fits)
 return(df_fit) 
}
```

# Checking assumptions 

### Performing Bartlett's test of sphericity

```{r}
(parameters::check_sphericity(fss)) 
```

 - Obs: We didn't use *bartlett.test()* because it performs homogeneity of variances

### Performing Kaiser, Meyer, Olkin (KMO) based on Measure of Sampling Adequacy (MSA)

```{r}
(kmo_mod <- KMO(fss)) 
```

### Evaluating normality

```{r}
(mvn_mod <- MVN::mvn(fss))
```

### Summarizing assumptions to perform analysis

```{r}
df <- cbind(mvn_mod$Descriptives[,c("Mean","Median","Std.Dev")]
            , "MSAi"=as.numeric(kmo_mod$MSAi)
            , "Statistic"=as.numeric(mvn_mod$univariateNormality$Statistic)
            , mvn_mod$Descriptives[,c("Skew","Kurtosis")]
            , mvn_mod$univariateNormality[,c("p value","Normality")])
knitr::kable(df, digits = 3)
```

# Exploratory Factorial Analysis (EFA)

Performing parallel factorial analysis

```{r}
if (!file.exists("pfa_mod.RData")) {
  pfa_mod <- fa.parallel(fss, fm = 'wls', fa = 'fa', cor='poly', plot = F)
  save(pfa_mod, file = "pfa_mod.RData")
}
load("pfa_mod.RData")
(pfa_mod)
```

```{r}
plot(pfa_mod)
```

Running EFA with the factors sugested by the parallel factorial analysis.

```{r}
efa_mod <- fa(fss, nfactors = pfa_mod$nfact, cor = 'poly', fm = 'wls')
print(loadings(fa.sort(efa_mod)), cutoff = 0.3)
```

Running EFA with nine (09) factors sugested by the parallel factorial analysis.

```{r}
efa_mod <- fa(fss, nfactors = 9, cor = 'poly', fm = 'wls')
print(loadings(fa.sort(efa_mod)), cutoff = 0.3)
```

# Construct validity

As there is not normality in the results, we decided to use the mean- and variance-adjusted weighted least squares (WLSMV) estimator, based on that WLSMV does not assume normal variables and it is a robust estimator developed to model categorical or ordered data (our case 5-likert scale).

 * Brown, T. (2006). Confirmatory factor analysis for applied research. New York: Guildford.
 * Proitsi, P., et al. (2009). A multiple indicators multiple causes (MIMIC) model of behavioural and psychological symptoms in dementia (BPSD). Neurobiology Aging. doi:10.1016/j.neurobiolaging.2009.03.005

## Multicorrelated models

### Multicorrelated nine factor original model

```{r}
Modelo1a <- '
CSB =~ Q1 + Q10 + Q19 + Q28
MAA =~ Q2 + Q11 + Q20 + Q29
CG  =~ Q3 + Q12 + Q21 + Q30
UF  =~ Q4 + Q13 + Q22 + Q31
CTH =~ Q5 + Q14 + Q23 + Q32
SC  =~ Q6 + Q15 + Q24 + Q33
LSC =~ Q7 + Q16 + Q25 + Q34
TT  =~ Q8 + Q17 + Q26 + Q35
AE  =~ Q9 + Q18 + Q27 + Q36

CSB ~~ MAA
CSB ~~ CG
CSB ~~ UF
CSB ~~ CTH
CSB ~~ SC
CSB ~~ LSC
CSB ~~ TT
CSB ~~ AE

MAA ~~ CG
MAA ~~ UF
MAA ~~ CTH
MAA ~~ SC
MAA ~~ LSC
MAA ~~ TT
MAA ~~ AE

CG ~~ UF
CG ~~ CTH
CG ~~ SC
CG ~~ LSC
CG ~~ TT
CG ~~ AE

UF ~~ CTH
UF ~~ SC
UF ~~ LSC
UF ~~ TT
UF ~~ AE

CTH ~~ SC
CTH ~~ LSC
CTH ~~ TT
CTH ~~ AE

SC ~~ LSC
SC ~~ TT
SC ~~ AE

LSC ~~ TT
LSC ~~ AE

TT ~~ AE
'

fit1a <-cfa(Modelo1a, data=fss, estimator="WLSMV", std.lv=TRUE)
summary(fit1a, fit.measures=TRUE)
```

*Observations (**fit indexes**)*:

 - CFI and TLI do not achieve 0.90s values.

```{r}
reliability(fit1a, return.total = TRUE)
```

*Observations (**reliability**)*:

 - less than 0.60 in CSB and CG.

```{r}
convergentDiscriminantValidity(fit1a, Modelo1a, fss)
```

*Observations (**convergent and discriminant validity**)*:

 - Composite Reliability less than 0.60 in CSB and CG
 - Based on the HTMT0.85 rule dicriminant are inadequate for CSB~AE CG~UF CG~SC UF~SC CTH~SC TT~AE.


### Multicorrelated nine factor model - fixed convergence and discriminant

Based on the EFA, the following values should be observed:

 - In the `CSB`, the items `Q1+Q10`  or `Q19` or `Q28`
 - In the  `TT`, the items `Q26+Q17` or `Q35` or `Q8`
 - In the  `AE`, the items `Q27`.    or `Q36` or `Q18` or `Q9`

Based on the HTMT0.85, the convergent and discriminant validity suggest combine:

 - (challenge-skill balance) CSB ~ AE (autotelic experience)
 - (clear goal) CG ~ UF (unambiguous feedback)
 - (transformation of time) TT ~ AE (autotelic experience)

```{r}
Modelo1b <- '
CSB =~ Q1 + Q10 + Q19
MAA =~ Q2 + Q11 + Q20 + Q29
CG  =~ Q3 + Q12 + Q21 
UF  =~ Q4 + Q13 + Q22 + Q31
CTH =~ Q5       + Q23 + Q32
SC  =~      Q15 + Q24 + Q33
LSC =~ Q7 + Q16 + Q25
TT  =~ Q8 + Q17 + Q26
AE  =~ Q9 + Q18 + Q27 

CSB ~~ MAA
CSB ~~ CG
CSB ~~ UF
CSB ~~ CTH
CSB ~~ SC
CSB ~~ LSC
CSB ~~ TT
CSB ~~ AE

MAA ~~ CG
MAA ~~ UF
MAA ~~ CTH
MAA ~~ SC
MAA ~~ LSC
MAA ~~ TT
MAA ~~ AE

CG ~~ UF
CG ~~ CTH
CG ~~ SC
CG ~~ LSC
CG ~~ TT
CG ~~ AE

UF ~~ CTH
UF ~~ SC
UF ~~ LSC
UF ~~ TT
UF ~~ AE

CTH ~~ SC
CTH ~~ LSC
CTH ~~ TT
CTH ~~ AE

SC ~~ LSC
SC ~~ TT
SC ~~ AE

LSC ~~ TT
LSC ~~ AE

TT ~~ AE
'

fit1b <-cfa(Modelo1b, data=fss, estimator="WLSMV", std.lv=TRUE)
summary(fit1b, fit.measures=TRUE)
```

*Observations (**fit indexes**)*:

 - TLI does not achieve 0.90s value but its close with 0.885

```{r}
reliability(fit1b, return.total = TRUE)
```

*Observations (**reliability**)*:

 - less than 0.60 in CSB and AE (but close to 0.60 with 0.59)


```{r}
convergentDiscriminantValidity(fit1b, Modelo1b, fss)
```

*Observations (**convergent and discriminant validity**)*:

 - Composite Reliability of CSB is 0.597 (close to 0.60s)
 - Based on the HTMT0.85 rule dicriminant are inadequate only for CG~UF

### Multicorrelated eight factor model - merging CG~UF

```{r}
Modelo1c <- '
CSB =~    Q1 + Q10 + Q19
MAA =~    Q2 + Q11 + Q20 + Q29
CG_UF  =~ Q3 + Q12 + Q21       + Q4 + Q13 + Q22 + Q31
CTH =~    Q5       + Q23 + Q32
SC  =~         Q15 + Q24 + Q33
LSC =~    Q7 + Q16 + Q25
TT  =~    Q8 + Q17 + Q26
AE  =~    Q9 + Q18 + Q27

CSB ~~ MAA
CSB ~~ CG_UF
CSB ~~ CTH
CSB ~~ SC
CSB ~~ LSC
CSB ~~ TT
CSB ~~ AE

MAA ~~ CG_UF
MAA ~~ CTH
MAA ~~ SC
MAA ~~ LSC
MAA ~~ TT
MAA ~~ AE

CG_UF ~~ CTH
CG_UF ~~ SC
CG_UF ~~ LSC
CG_UF ~~ TT
CG_UF ~~ AE

CTH ~~ SC
CTH ~~ LSC
CTH ~~ TT
CTH ~~ AE

SC ~~ LSC
SC ~~ TT
SC ~~ AE

LSC ~~ TT
LSC ~~ AE

TT ~~ AE
'

fit1c <-cfa(Modelo1c, data=fss, estimator="WLSMV", std.lv=TRUE)
summary(fit1c, fit.measures=TRUE)
```

*Observations (**fit indexes**)*:

 - TLI does not achieve 0.90s value but its close with 0.888

```{r}
reliability(fit1c, return.total = TRUE)
```

*Observations (**reliability*)*:

 - less than 0.60 in CSB and AE (but close to 0.60s with 0.59)

```{r}
convergentDiscriminantValidity(fit1c, Modelo1c, fss)
```

*Observations (**convergent and discriminant validity**)*:

 - Composite Reliability of CSB is 0.597 (close to 0.60s)


## 2nd-order factor models

### 2nd-order nine factor original model

```{r}
Modelo2a <- '
CSB =~ Q1 + Q10 + Q19 + Q28
MAA =~ Q2 + Q11 + Q20 + Q29
CG  =~ Q3 + Q12 + Q21 + Q30
UF  =~ Q4 + Q13 + Q22 + Q31
CTH =~ Q5 + Q14 + Q23 + Q32
SC  =~ Q6 + Q15 + Q24 + Q33
LSC =~ Q7 + Q16 + Q25 + Q34
TT  =~ Q8 + Q17 + Q26 + Q35
AE  =~ Q9 + Q18 + Q27 + Q36

FSS  =~ CSB + MAA + CG + UF + CTH + SC + LSC + TT + AE

CSB ~~ 0*MAA
CSB ~~ 0*CG
CSB ~~ 0*UF
CSB ~~ 0*CTH
CSB ~~ 0*SC
CSB ~~ 0*LSC
CSB ~~ 0*TT
CSB ~~ 0*AE

MAA ~~ 0*CG
MAA ~~ 0*UF
MAA ~~ 0*CTH
MAA ~~ 0*SC
MAA ~~ 0*LSC
MAA ~~ 0*TT
MAA ~~ 0*AE

CG ~~ 0*UF
CG ~~ 0*CTH
CG ~~ 0*SC
CG ~~ 0*LSC
CG ~~ 0*TT
CG ~~ 0*AE

UF ~~ 0*CTH
UF ~~ 0*SC
UF ~~ 0*LSC
UF ~~ 0*TT
UF ~~ 0*AE

CTH ~~ 0*SC
CTH ~~ 0*LSC
CTH ~~ 0*TT
CTH ~~ 0*AE

SC ~~ 0*LSC
SC ~~ 0*TT
SC ~~ 0*AE

LSC ~~ 0*TT
LSC ~~ 0*AE

TT ~~ 0*AE
'

fit2a <-cfa(Modelo2a, data=fss, estimator="WLSMV", std.lv=TRUE)
summary(fit2a, fit.measures=TRUE)
```

*Observations (**fit indexes**)*:

 - CFI and TLI do not achieve 0.90s values.

```{r}
reliability(fit2a, return.total = TRUE)
reliabilityL2(fit2a, "FSS")
```

*Observations (**reliability**)*:

 - less than 0.60 in CSB and CG.

```{r}
convergentDiscriminantValidity(fit2a, Modelo2a, fss, "FSS")
```

*Observations (**convergent and discriminant validity**)*:

 - Composite Reliability less than 0.60 in CSB and CG
 - Based on the HTMT0.85 rule dicriminant are inadequate for CSB~AE CG~UF CG~SC UF~SC CTH~SC TT~AE.


### 2nd-order eight factor model - fixed convergence and discriminant

Based on the EFA, the following values should be observed:

 - In the `CSB`, the items `Q1+Q10`  or `Q19` or `Q28`
 - In the  `TT`, the items `Q26+Q17` or `Q35` or `Q8`
 - In the  `AE`, the items `Q27`.    or `Q36` or `Q18` or `Q9`

Based on the HTMT0.85, the convergent and discriminant validity suggest combine:

 - (challenge-skill balance) CSB ~ AE (autotelic experience)
 - (clear goal) CG ~ UF (unambiguous feedback)
 - (transformation of time) TT ~ AE (autotelic experience)

```{r}
Modelo2b <- '
CSB =~ Q1 + Q10 + Q19
MAA =~ Q2 + Q11 + Q20 + Q29
CG  =~ Q3 + Q12 + Q21 
UF  =~ Q4 + Q13 + Q22 + Q31
CTH =~ Q5       + Q23 + Q32
SC  =~      Q15 + Q24 + Q33
LSC =~ Q7 + Q16 + Q25
TT  =~ Q8 + Q17 + Q26
AE  =~ Q9 + Q18 + Q27 

FSS  =~ CSB + MAA + CG + UF + CTH + SC + LSC + TT + AE

CSB ~~ 0*MAA
CSB ~~ 0*CG
CSB ~~ 0*UF
CSB ~~ 0*CTH
CSB ~~ 0*SC
CSB ~~ 0*LSC
CSB ~~ 0*TT
CSB ~~ 0*AE

MAA ~~ 0*CG
MAA ~~ 0*UF
MAA ~~ 0*CTH
MAA ~~ 0*SC
MAA ~~ 0*LSC
MAA ~~ 0*TT
MAA ~~ 0*AE

CG ~~ 0*UF
CG ~~ 0*CTH
CG ~~ 0*SC
CG ~~ 0*LSC
CG ~~ 0*TT
CG ~~ 0*AE

UF ~~ 0*CTH
UF ~~ 0*SC
UF ~~ 0*LSC
UF ~~ 0*TT
UF ~~ 0*AE

CTH ~~ 0*SC
CTH ~~ 0*LSC
CTH ~~ 0*TT
CTH ~~ 0*AE

SC ~~ 0*LSC
SC ~~ 0*TT
SC ~~ 0*AE

LSC ~~ 0*TT
LSC ~~ 0*AE

TT ~~ 0*AE
'

fit2b <-cfa(Modelo2b, data=fss, estimator="WLSMV", std.lv=TRUE)
summary(fit2b, fit.measures=TRUE)
```

*Observations (**fit indexes**)*:

 - CFI and TLI does not achieve 0.90s values

```{r}
reliability(fit2b, return.total = TRUE)
reliabilityL2(fit2b, "FSS")
```

*Observations (**reliability**)*:

 - less than 0.60 in CSB and AE (but close to 0.60 with 0.59)


```{r}
convergentDiscriminantValidity(fit2b, Modelo2b, fss, "FSS")
```

*Observations (**convergent and discriminant validity**)*:

 - Composite Reliability of CSB is 0.597 (close to 0.60s)
 - Based on the HTMT0.85 rule dicriminant are inadequate only for CG~UF

### 2nd-order eight factor model - merging CG~UF

```{r}
Modelo2c <- '
CSB =~    Q1 + Q10 + Q19
MAA =~    Q2 + Q11 + Q20 + Q29
CG_UF  =~ Q3 + Q12 + Q21       + Q4 + Q13 + Q22 + Q31
CTH =~    Q5       + Q23 + Q32
SC  =~         Q15 + Q24 + Q33
LSC =~    Q7 + Q16 + Q25
TT  =~    Q8 + Q17 + Q26
AE  =~    Q9 + Q18 + Q27

FSS  =~ CSB + MAA + CG_UF + CTH + SC + LSC + TT + AE

CSB ~~ 0*MAA
CSB ~~ 0*CG_UF
CSB ~~ 0*CTH
CSB ~~ 0*SC
CSB ~~ 0*LSC
CSB ~~ 0*TT
CSB ~~ 0*AE

MAA ~~ 0*CG_UF
MAA ~~ 0*CTH
MAA ~~ 0*SC
MAA ~~ 0*LSC
MAA ~~ 0*TT
MAA ~~ 0*AE

CG_UF ~~ 0*CTH
CG_UF ~~ 0*SC
CG_UF ~~ 0*LSC
CG_UF ~~ 0*TT
CG_UF ~~ 0*AE

CTH ~~ 0*SC
CTH ~~ 0*LSC
CTH ~~ 0*TT
CTH ~~ 0*AE

SC ~~ 0*LSC
SC ~~ 0*TT
SC ~~ 0*AE

LSC ~~ 0*TT
LSC ~~ 0*AE

TT ~~ 0*AE
'

fit2c <-cfa(Modelo2c, data=fss, estimator="WLSMV", std.lv=TRUE)
summary(fit2c, fit.measures=TRUE)
```

*Observations (**fit indexes**)*:

 - CFI and TLI does not achieve 0.90s value but its close with 0.888

```{r}
reliability(fit2c, return.total = TRUE)
reliabilityL2(fit2c, "FSS")
```

*Observations (**reliability*)*:

 - less than 0.60 in CSB and AE (but close to 0.60s with 0.59)

```{r}
convergentDiscriminantValidity(fit2c, Modelo2c, fss, 'FSS')
```

*Observations (**convergent and discriminant validity**)*:

 - Composite Reliability of CSB is 0.599 (close to 0.60s)

## Unidimensional models (Short version of FSS-BR)

### Original short version of FSS-BR (FSS-short)

```{r}
Modelo3a <- 'FSS =~ Q19 + Q29 + Q12 + Q22 + Q32 + Q6 + Q7 + Q17 + Q36'

fit3a <-cfa(Modelo3a, data=fss, estimator="WLSMV", std.lv=TRUE)
summary(fit3a, fit.measures=TRUE)
```

*Observations (**fit indexes**)*:

 - CFI and TLI does not achieve 0.90s value 

```{r}
reliability(fit3a, return.total = TRUE)
```

*Observations (**reliability*)*:

 - less than 0.60


### Alternative short version of FSS-BR (alt FSS-short)

To elaborate this version, we replaced the items from the original short version
that doesn't have item loadings close or high to the value of 0.7 in the long version of the FSS-BR.
Thus, we performed the following changes:

- In the CSB, the item Q19 was replaced for Q10.
- In the MAA, the item Q29 was replaced for Q11.
- In the CG,  the item Q12 was replaced for Q21.
- In the UF,  the item Q22 was replaced for Q4.
- In the SC,  the item Q6  was replaced for Q24.
- In the AE,  the item Q36 was replaced for Q27.
- For the rest of factors CTH, LSC and TT  the items Q32, Q7 and Q17 were maintained.

```{r}
Modelo3b <- 'FSS =~ Q10 + Q11 + Q21 + Q4 + Q32 + Q24 + Q7 + Q17 + Q27'

fit3b <-cfa(Modelo3b, data=fss, estimator="WLSMV", std.lv=TRUE)
summary(fit3b, fit.measures=TRUE)
```


```{r}
reliability(fit3b, return.total = TRUE)
```

## Summary of construct validity (structural, reliability and convergent/discriminant)

### Structural validity - CFAs

```{r}
df <- summariseFits(list('nine-multicorrelated model'=fit1a
                         ,'nine-multicorrelated model (with removed items)'=fit1b
                         , 'eight-multicorrelated model (with removed items)'=fit1c
                         , '2nd-order nine-factor model'=fit2a
                         , '2nd-order nine-factor model (with removed items)'=fit2b
                         , '2nd-order eight-factor model (with removed items)'=fit2c
                         , 'unidimensional model (short)'=fit3a
                         , 'unidimensional model (alt short)'=fit3b))
knitr::kable(df, digits = 3)
```

*Observations (**fit indexes**)*:

 - Original nine-multicorrelated model doesn't have adequate fit indexes
 - None of 2nd-order models have adequate `srmr` (all values are greater than `0.10`)
 - The nine-multicorrelated model and eight-multicorrelated model with some removed items, both models have good fit indexes
 - Only the alternative version of FSS-BR have good fit

Running anova test to compare fit indexes in the nine-multicorrelated and eight-multicorrelated CFA models with some removed items

```{r}
lavTestLRT(fit1b, fit1c, model.names=c('nine-multicorr','eight-multicorr'))
```

*Observations (**comparing models**)*:

 - Pr(>Chisq) is not significat => there is not difference between both models
 - Both models give proper results (by flow theory - we sugest use the nine-multicorrelated model)

### Reliability validity - Cronbach / Omega / CR

nine-multicorrelated model with some removed items

```{r}
df <- rbind(reliability(fit1b, return.total = T)
            , "CR"=compReliability(fit1b, return.total = T))
knitr::kable(df, digits = 3)
```

Eight-multicorrelated model with some removed items

```{r}
df <- rbind(reliability(fit1c, return.total = T)
            , "CR"=compReliability(fit1c, return.total = T))
knitr::kable(df, digits = 3)
```

Alternative short version of FSS-BR

```{r}
df <- rbind(reliability(fit3b), "CR"=compReliability(fit3b))
knitr::kable(t(df), digits = 3)
```

### Convergent and discriminant validity

nine-multicorrelated model with some removed items

```{r}
df <- convergentDiscriminantValidity(fit1b, Modelo1b, fss)
knitr::kable(df, digits = 3)
```

Eight-multicorrelated model with some removed items

```{r}
df <- convergentDiscriminantValidity(fit1c, Modelo1c, fss)
knitr::kable(df, digits = 3)
```

*Observations (**convergent and discriminant validity**)*:

 - If AVE is less than 0.5, but CR is higher than 0.6 in all the factors, the convergent validity of the construct is still adequate (Fornell & Larcker, 1981).
 - If the VIF > 5, there is mulcollinearity issues in the dataset. The possible solutions are:
  Remove items with maximal VIF in the items for factors (VFI.i); or combine constructs with more than .80 or .85  correlation values.
 - The lower triangualar part of the table corresponds with correlations between factors. The square root of AVE is located in the diagonally of the matrix. For discriminate validity, the diagonal elements should be larger than the off-diagonal elements (correlations for factors).
 - The upper triangular part of the table displays the heterotrait-monotrait ratio (HTMT) of the correlations (Henseler, Ringlet & Sarstedt, 2015). Lower values indicate higher levels of discriminant validity. HTMT values greater than 0.85 (> 0.85) indicate discriminant validity issues.


# Item quality analysis based on IRT (Item Response Theory)

Loadings fss data for performing IRT analysis

```{r}
ls <- as.data.frame(standardizedSolution(fit1b))
ls <- ls[ls$op == '=~',]

fss2 <- fss[,ls$rhs]
```

## IRT analysis in the long version of the DFS-BR


```{r}
dados_tri<-mirt(fss2, 1, itemtype='graded')
```

### Estimate parameters

```{r}
params <- coef(dados_tri, simplify=TRUE, IRTpars=TRUE)
knitr::kable(params$items, digits = 3)
```

### Graphs of test information curve

```{r, fig.width=12}
plot(dados_tri, type='infotrace')
```

```{r, fig.width=12}
plot(dados_tri, type='info')
```

Graph of Test Information and Standard Errors

```{r, fig.width=12}
plot(dados_tri, type='infoSE')
```

## IRT analysis in the short version of the alt FSS-BR


Loadings fss data for performing IRT analysis

```{r}
ls <- as.data.frame(standardizedSolution(fit3b))
ls <- ls[ls$op == '=~',]

fss3 <- fss[,ls$rhs]
```

```{r}
dados_tri3 <-mirt(fss3, 1, itemtype='graded')
```

### Estimate parameters

```{r}
params3 <- coef(dados_tri3, simplify=TRUE, IRTpars=TRUE)
knitr::kable(params3$items, digits=3)
```

### Graphs of test information curve

```{r,fig.width=12}
plot(dados_tri3,type='infotrace')
```

```{r,fig.width=12}
plot(dados_tri3,type='info')
```

Graph of Test Information and Standard Errors

```{r, fig.width=12}
plot(dados_tri3,type='infoSE')
```





-------------
```{r, echo=FALSE}

```
